\documentclass[a4paper, 12pt]{letter}

\usepackage[utf8]{inputenc}
\usepackage[margin=2.5cm]{geometry}
%\usepackage[MeX]{polski}
\longindentation=0.65\textwidth
\begin{document}
\begin{letter}{Samsung Poland R\&D Center\\Al. Bora-Komorowskiego 25\\31-476 Kraków}
\address{Maciej Kopeć\\Brogi~40/107\\31-431~Kraków}

\opening{Dear Sir or Madam,}

In response to~your job opening, I would like to~place my candidature.

I am a~young, eager to learn student in my fifth year at~the~AGH-UST doing~a~degree in~technical physics. Electronics and~embedded systems are my passion, which is the~main reason why, I~think, I would be a~perfect candidate for the~posted opening.

During my internship at Woodward Poland, I was responsible for many electronics-related tasks. I~prepared setups, performed tests and then analyzed the~results. I~also designed electrical circuits and a~few PCBs. Throughout my work, in many areas, I was an independent engineer and~solved problems myself without any guidance. What is more, there were some ideas of mine, which were accepted and~used more generally, in bigger projects.

The~above is not my only experience with designing electronics on~the~schematic level. I~made numerous hobbystic projects, which I designed from schematic to a~PCB. Some of~the projects were made on a~prototype board, some on~a~universal PCB and some were produced by a~PCB manufacturer. During courses at the~university, I also designed and simulated integrated circuits, such as an operation amplifier or a Digital-to-Analog Converter. Both projects achieved maximum grades. What is more, the~DAC was designed with 2-bit better resolution (compared to~the~rest of~the~students group) and~the~same acceptable error rates, which made the project even more challenging. Both ICs were layouted and tested afterwards as well.

While I am not afraid of analog electronics, it is not my strongest side and I realize there is still much to learn. I am eager to do that and I really find analog circuit designing pleasant. All in all, my strongest side is~the~digital electronics. The~most fascinating topics for me in this category are data transmission protocols. Their hardware and software implementation is the thing, I enjoy the most. My recent work in this area is my master's thesis, for which I am developing a~hardware I\textsuperscript{2}C protocol implementation. It will be a~part of~a readout electronics chip for CERN, Geneva. Most of~my work in~digital electronics is based on Verilog HDL. For my master's thesis I will also get to know System Verilog. What is more I prepared several projects on Xilinx Spartan-3AN Starter Kit during one of~the~courses at the~university.

Designing electronics is not my only asset. I have plenty of~experience in programming. Earlier I~was working in web-development, and recently embedded systems, especially microcontrollers. I used ATmega and ARM cores and developed a~few applications. The biggest and the~most complicated was my bachelor's thesis. In all microcontroller-based projects I used ANSI~C. I find bringing a~tiny computer to life very exciting and enjoyable. This is definitely one of my favorite activities and~I~tend to have a~lot of~ideas for microcontroller applications.

To sum up, there are areas in electronics, which I like a~lot, some of~the design process I~like a~little less, but there is no better feeling in the world, than looking at a~finished, working product, which was developed with hard work. Nothing makes one more proud than seeing this.

\vspace{4\baselineskip}

\signature{\vspace{-3\baselineskip}Maciej Kopeć}

\closing{Yours faithfully,}

%enclosure listing
%\encl{}

\end{letter}
\end{document}
