% !TeX spellcheck = en_US
\documentclass[11pt,a4paper,sans]{moderncv}

%% Character encoding
\usepackage[utf8]{inputenc}
\usepackage{graphicx}

%% ModernCV themes
\moderncvstyle{classic}
\moderncvcolor{blue}
%\renewcommand{\familydefault}{\sfdefault}
\nopagenumbers{}

% Japanese
\usepackage{CJKutf8}

% Russian
%\usepackage[russian]{babel}

%% Adjust the page margins
\usepackage[margin=1.8cm]{geometry}
\setlength{\hintscolumnwidth}{3.5cm}

\newcommand{\mycvitemwithcomment}[3]{\cvitemwithcomment{\parbox{0.2\textwidth}{\vspace{-\baselineskip}\flushright #1}}{\parbox{10cm}{#2}}{#3}\vspace{0.5\baselineskip}}

%% Personal data
\firstname{Maciej P.}
\familyname{Kopeć}
\address{Na Popielówkę 75P/2}{32-087 Zielonki, Poland}
\mobile{+48 515 083 938}
\email{maciej.p.kopec@gmail.com}
\extrainfo{Date of birth: 11\textsuperscript{th} April 1991}
%\photo[80pt][0.4pt]{mkopec.jpg}

%%------------------------------------------------------------------------------
%% Content
%%------------------------------------------------------------------------------
\begin{document}
\makecvtitle

\section{Education}
\cventry{2015--2016}{PhD}{AGH-UST}{Cracow}{interrupted}{Major: \textbf{Physics} 
at Faculty of Physics and Applied Computer Science}
\cventry{2014--2015}{MSc}{\textbf{AGH-UST}}{\textbf{Cracow}}{5.0}{Major: \textbf{Technical Physics} at~Faculty of~Physics and~Applied Computer Science}
\cventry{2010--2014}{BSc}{\textbf{AGH-UST}}{\textbf{Cracow}}{\textit{4.5}}{Major: \textbf{Technical Physics} at~Faculty of~Physics and~Applied Computer Science}

\section{Professional experience}
\cventry{April 2019 -- present}{Electronics Engineer}{Merit Poland sp. z 
o.o}{}{}{}
\cvlistitem{Electronic circuit design for automotive.}
\cvlistitem{Simulations and data analysis.}
\cvlistitem{Component database maintenance.}
\cvlistitem{Development of ECAD tools integration process.}
\cvlistitem{Tests and measurements.}
\cvlistitem{Design and requirements analysis.}
\cvlistitem{Supporting interns in their development.}

\cventry{January 2018 -- March 2019}{Electronics Engineer}{Sii Poland}{}{}{}
\vspace{-\baselineskip}
\cvlistitem{Electronic circuit design for automotive.}
\cvlistitem{Simulations and data analysis.}
\cvlistitem{Component database maintenance.}
\cvlistitem{Tests and measurements.}
\cvlistitem{Design and requirements analysis.}
\cvlistitem{Supporting interns in their development.}

\cventry{December 2014 -- December 2017}{Beam diagnostics and Instrumentation Specialist}{National Synchrotron Radiation Centre `Solaris'}{}{}{}
\cvlistitem{Electronic readout and measurement systems design.}
\cvlistitem{Design for manufacture and proper mechanical integration.}
\cvlistitem{Electronic prototyping and reworking.}
\cvlistitem{Beam instrumentation design, maintenance, diagnostics and assembly.}
\cvlistitem{Diagnostic data analysis.}
\cvlistitem{Design simulations and simulation data analysis automation}
\cvlistitem{Diagnostic equipment related IT works --- scripting, setup in 
the~network, etc.}

\cventry{May 2016 -- \linebreak August 2016}{Embedded systems developer}{Organisation Européenne pour la Recherche Nucléaire (CERN)}{}{}{}
\cvlistitem{Development of 1G ethernet link on ZC706 evaluation board \newline using Zynq SoC}
\cvlistitem{Detector readout systems testing and debugging}
\cvlistitem{Setting up development environments for detector readout systems}

\cventry{January 2014 -- \linebreak June 2014}{Hardware development intern}{Woodward Poland sp. z o.o.}{}{}{}
\vspace{-\baselineskip}
\cvlistitem{Electrical circuit design.}
\cvlistitem{Working with PCB prototypes (e.g. soldering under a~microscope, 
test 
preparation).}
\cvlistitem{Measurements and~data analysis.}
\cvlistitem{RoHS directive compliance verification.}

\cventry{July 2013 -- \linebreak August 2013}{Electrical engineering trainee}{Faculty of~Physics and~Applied Computer Science}{}{}{}
\vspace{-\baselineskip}
\cvlistitem{Programming microcontrollers with ARM Cortex-M3 core.}

\cventry{2008--2013}{Web-developer}{Back-end and front-end web development}{}{}{}
\cvlistitem{HTML, CSS and jQuery front-end development.}
\cvlistitem{Preparing custom templates for Wordpress.}
\cvlistitem{Writing plugins and snippets for CMS systems(Wordpress, Joomla).}


\section{Courses and certificates}

%\mycvitemwithcomment{In progress}{Advanced PCB Layout Course}{FEDEVEL~Academy}
%\vspace{-.5\baselineskip}
\mycvitemwithcomment{November 2018}{EMC for automotive \hspace{-7.5cm}}{EMC 
Solution}
\vspace{-.5\baselineskip}
\mycvitemwithcomment{October 2017}{Advanced Hardware Design 
\hspace{-7.5cm}}{FEDEVEL~Academy}
\vspace{-.5\baselineskip}
\mycvitemwithcomment{June 2017}{Accelerator Power Electronics 
Engineering (Grade: Excellent)}{USPAS June 2017}
\vspace{-.5\baselineskip}
\mycvitemwithcomment{June 2017}{Pulsed Power Engineering (Grade: 
Outstanding)}{USPAS June 2017}
\vspace{-.5\baselineskip}
\mycvitemwithcomment{December 2016}{Learn Altium Essentials}{FEDEVEL~Academy}
\vspace{-.5\baselineskip}
\mycvitemwithcomment{April 2016}{PCB design at RF --- multi-Gigabit 
transmission, EMI control and PCB materials}{Cadence GmbH}
\vspace{-.5\baselineskip}
\mycvitemwithcomment{April 2016}{Essential high-speed PCB design for signal integrity}{Cadence GmbH}
\vspace{-.5\baselineskip}

\section{Recent publications}
\cvlistitem{M.P. Kopeć et~al., \emph{Universal digital aggregator for in-line 
signal processing}, 
IPAC~2017}

\cvlistitem{A.I. Wawrzyniak et~al., \emph{Performance of Solaris storage 
ring}, IPAC 2017}
\cvlistitem{ A. Kisiel et~al., \emph{Beta function measurement in the Solaris 
storage ring}, IPAC 2017}

\section{University and private projects}
\cventry{July 2014 -- \\Sptember 2015}{Master thesis}{}{}{}{{\large Subject: Control interface for SALT ASIC for LHCb detector tracker upgrade}}
\cvlistitem{Hardware I\textsuperscript{2}C interface implementation in Verilog.}

\cventry{July 2013 -- \\ October 2013}{Bachelor thesis}{}{}{}{{\large Subject: Demo application for colour touchscreen working in embedded system}}
\cvlistitem{Design and~implementation of~GUI library for~LPC1768 microcotroller 
with a~demo application.}

\section{Other skills}

\cvitemwithcomment{\parbox{0.2\textwidth}{\vspace{-\baselineskip}\flushright 
Programming languages}}{\parbox{13cm}{C, C++ (basic), Python, Verilog, 
SystemVerilog, LabView (basic), VHDL, SQL (more than basic), MATLAB (basic), 
Simulink(basic)}}{}
\vspace{0.5\baselineskip}
\cvitemwithcomment{Design software}{\parbox{13cm}{KiCad, EAGLE 6 (schematic 
and~layout), Altium Designer, Mentor Graphics xPCB Design Flow, LTspice IV, 
Xilinx ISE, Xilinx Vivado (more than basic), Xilinx SDK (basic), Keil uVision, 
Atmel Studio, Eclipse}}{}
\vspace{0.5\baselineskip}
\cvitemwithcomment{\parbox{0.2\textwidth}{\vspace{-\baselineskip}\flushright 
Other software and~technologies}}{\parbox{13cm}{Linux, \LaTeX, git, Wordpress, 
MS Office}}{}
\vspace{0.5\baselineskip}
\cvitemwithcomment{\parbox{0.2\textwidth}{\vspace{-\baselineskip}\flushright 
Additional qualifications}}{\parbox{13cm}{SEP 1\hspace{3pt}kV~license 
(30\hspace{3pt}kV for laboratory testing), driving 
license, good knowledge of~circuits and~signals theory, coping with 
analytical problems}}{}

\section{Languages}

\cvitemwithcomment{English}{Fluent (FCE passed in 2007)}{}
\cvitemwithcomment{Russian}{Basic}{}
\cvitemwithcomment{Japanese}{Semi-intermediate}{Learning in progress}

\section{Interests}

\cvlistitem{volleyball, cycling, books, DIY, snooker, e-sports, physics.}

\section{Disclaimer}

I agree to the processing of personal data provided in this document for 
realising the recruitment process pursuant to the Personal Data Protection Act 
of 10 May 2018 (Journal of Laws 2018, item 1000) and in agreement with 
Regulation (EU) 2016/679 of the European Parliament and of the Council of 27 
April 2016 on the protection of natural persons with regard to the processing 
of personal data and on the free movement of such data, and repealing Directive 
95/46/EC (General Data Protection Regulation).


\bibliography{publications}
\end{document}