% !TeX spellcheck = en_US
\documentclass[11pt,a4paper,sans]{moderncv}

%% Character encoding
\usepackage[utf8]{inputenc}
\usepackage{graphicx}

%% ModernCV themes
\moderncvstyle{classic}
\moderncvcolor{blue}
%\renewcommand{\familydefault}{\sfdefault}
\nopagenumbers{}

% Japanese
\usepackage{CJKutf8}

% Russian
%\usepackage[russian]{babel}

%% Adjust the page margins
\usepackage[margin=1.8cm]{geometry}
\setlength{\hintscolumnwidth}{3.5cm}

\newcommand{\mycvitemwithcomment}[3]{\cvitemwithcomment{\parbox{0.2\textwidth}{\vspace{-\baselineskip}\flushright #1}}{\parbox{10cm}{#2}}{#3}\vspace{0.5\baselineskip}}

%% Personal data
\firstname{Maciej P.}
\familyname{Kopeć}
\address{Na Popielówkę 75P/2}{32-087 Zielonki, Poland}
\mobile{+48 515 083 938}
\email{maciej.p.kopec@gmail.com}
\extrainfo{Date of birth: 11\textsuperscript{th} April 1991}
%\photo[80pt][0.4pt]{mkopec.jpg}

%%------------------------------------------------------------------------------
%% Content
%%------------------------------------------------------------------------------
\begin{document}
\makecvtitle

\section{Education}
\cventry{2015--2016}{PhD}{AGH-UST}{Cracow}{}{Major: \textbf{Physics} at Faculty of Physics and Applied Computer Science}
\cventry{2014--2015}{MSc}{\textbf{AGH-UST}}{\textbf{Cracow}}{5.0}{Major: \textbf{Technical Physics} at~Faculty of~Physics and~Applied Computer Science}
\cventry{2010--2014}{BSc}{\textbf{AGH-UST}}{\textbf{Cracow}}{\textit{4.5}}{Major: \textbf{Technical Physics} at~Faculty of~Physics and~Applied Computer Science}

\section{Professional experience}
\cventry{December 2014 -- \linebreak present}{Beam diagnostics and Instrumentation Specialist}{National Synchrotron Radiation Centre `Solaris'}{}{}{}
\cvlistitem{Electronic readout and measurement systems design.}
\cvlistitem{Design for manufacture and cases.}
\cvlistitem{Electronic prototyping and reworking.}
\cvlistitem{Beam instrumentation diagnostics and assembly.}
\cvlistitem{Beam diagnostic equipment design and maintenance.}

\cventry{May 2016 -- \linebreak August 2016}{Embedded systems developer}{Organisation Européenne pour la Recherche Nucléaire (CERN)}{}{}{}
\cvlistitem{Development of 1G ethernet link on ZC706 evaluation board \newline using Zynq SoC}
\cvlistitem{Detector readout systems testing and debugging}
\cvlistitem{Setting up development environments for detector readout systems}

\cventry{January 2014 -- \linebreak June 2014}{Hardware development intern}{Woodward Poland sp. z o.o.}{}{}{}
\vspace{-\baselineskip}
\cvlistitem{Electrical circuit design.}
\cvlistitem{Working PCB prototypes (e.g. soldering under a~microscope, test 
preparation).}
\cvlistitem{Measurements and~data analysis.}
\cvlistitem{RoHS directive compliance verification.}

\cventry{July 2013 -- \linebreak August 2013}{Electrical engineering trainee}{Faculty of~Physics and~Applied Computer Science}{}{}{}
\vspace{-\baselineskip}
\cvlistitem{Programming microcontrollers with ARM Cortex-M3 core.}

\cventry{2008--2013}{Web-developer}{Back-end and front-end web development}{}{}{}
\cvlistitem{Preparing graphic files for HTML and CSS coding.}
\cvlistitem{HTML, CSS and jQuery front-end development.}
\cvlistitem{Preparing custom templates for Wordpress.}
\cvlistitem{Writing plugins and snippets for CMS systems(Wordpress, Joomla).}

\section{Courses and certificates}

\mycvitemwithcomment{In progress}{Advanced Hardware Design \hspace{-7.5cm}}{FEDEVEL~Academy}
\vspace{-.5\baselineskip}
\mycvitemwithcomment{In progress}{Advanced PCB Layout Course}{FEDEVEL~Academy}
\vspace{-.5\baselineskip}
\mycvitemwithcomment{June 2017}{Accelerator Power Electronics 
Engineering (Grade: Excellent)}{USPAS June 2017}
\vspace{-.5\baselineskip}
\mycvitemwithcomment{June 2017}{Pulsed Power Engineering (Greade: 
Outstanding)}{USPAS June 2017}
\vspace{-.5\baselineskip}
\mycvitemwithcomment{December 2016}{Learn Altium Essentials}{FEDEVEL~Academy}
\vspace{-.5\baselineskip}
\mycvitemwithcomment{April 2016}{PCB design at RF --- multi-Gigabit 
transmission, EMI control and PCB materials}{Cadence GmbH}
\vspace{-.5\baselineskip}
\mycvitemwithcomment{April 2016}{Essential high-speed PCB design for signal integrity}{Cadence GmbH}
\vspace{-.5\baselineskip}

\section{Last year publications}
\subsection{As a~corresponding author}
\cvlistitem{M.P. Kopeć et~al., \emph{Universal digital aggregator for in-line 
signal processing}, 
IPAC~2017}

\subsection{As a~co-author}
\cvlistitem{A.I. Wawrzyniak et~al., \emph{Performance of Solaris storage 
ring}, IPAC 2017}
\cvlistitem{ A. Kisiel et~al., \emph{Beta function measurement in the Solaris 
storage ring},IPAC 2017}

\section{University and private projects and~designs}
\cventry{July 2014 -- \\Sptember 2015}{Master thesis}{}{}{}{{\large Subject: Control interface for SALT ASIC for LHCb detector tracker upgrade}}
\cvlistitem{Hardware I\textsuperscript{2}C interface implementation in Verilog.}

\cventry{July 2013 -- \\ October 2013}{Bachelor thesis}{}{}{}{{\large Subject: Demo application for colour touchscreen working in embedded system}}
\cvlistitem{Design and~implementation of~GUI library for~LPC1768 microcotroller with a~demo application.}

\section{Languages}

\cvitemwithcomment{English}{Fluent (FCE)}{}
\cvitemwithcomment{Russian}{Basic}{}
\cvitemwithcomment{Japanese}{Basic}{Learning in progress}

\section{Other skills}

\cvitemwithcomment{\parbox{0.2\textwidth}{\vspace{-\baselineskip}\flushright Programming languages}}{\parbox{13cm}{C, C++ (basic), Python, Verilog, SystemVerilog, LabView (basic), VHDL, SQL (more than basic), MATLAB (basic), Simulink(basic)}}{}
\vspace{0.5\baselineskip}
\cvitemwithcomment{Design software}{\parbox{13cm}{KiCad, EAGLE 6 (schematic and~layout), Altium Designer, LTspice IV, Xilinx ISE, Xilinx Vivado (more than basic), Xilinx SDK (basic), Keil uVision, Atmel Studio, Eclipse}}{}
\vspace{0.5\baselineskip}
\cvitemwithcomment{\parbox{0.2\textwidth}{\vspace{-\baselineskip}\flushright Other software and~technologies}}{\parbox{13cm}{Linux, \LaTeX, git, Wordpress, MS Office}}{}
\vspace{0.5\baselineskip}
\cvitemwithcomment{\parbox{0.2\textwidth}{\vspace{-\baselineskip}\flushright Additional qualifications}}{\parbox{13cm}{SEP 1\hspace{3pt}kV~license, driving license, good knowledge of~circuits and~signals\newline theory, coping with analytical problems}}{}

\section{Interests}

\cvlistitem{volleyball, cycling, books, DIY, snooker, e-sports, physics.}

\section{Disclaimer}

I hereby authorize you to process my personal data included in my job application for
the needs of the recruitment process in accordance with the Personal Data
Protection Act dated 29.08.1997 (uniform text: Journal of Laws of the Republic of
Poland 2002 No 101, item 926 with further amendments)


\bibliography{publications}
\end{document}